\vspace{-1em}Guidance, please! Towards a framework for RDF-based constraint languages.

### 2015-07-18 paper/paper 2/dc-2015.tex
DL

\section{Towards a framework} 
\label{sec:vocabulary}

@@

\subsection{Building blocks}

At the core, we use a very simple conceptual model for constraints, using a small vocabulary called \emph{RDF Constraints Vocabulary (RDF-CV)}\footnote{Online available at: \url{https://github.com/boschthomas/RDF-Constraints-Vocabulary}}. The conceptual model is shown in Figure \ref{fig:RDF-CV-conceptual-model}.
\begin{figure}[H]
	\centering
		\includegraphics[width=0.80\textwidth]{images/RDF-CV.png}
	\caption{\emph{RDF Constraints Vocabulary (RDF-CV)} Conceptual Model}
	\label{fig:RDF-CV-conceptual-model}
\end{figure}

\emph{Simple constraints} denotes the set of atomic constraints with respect to a single constraining element -- we will come to the notion of a constraining element in a second. In contrast, there are  
\emph{complex constraints}, i.e., the set of constraints which are created out of \emph{simple} and/or other \emph{complex constraints}. This structure therefore allows to build complex constraints out of other (simple or complex) constraints. Regarding our database of constraint types, 60\% of the constraint types are simple constraints and 26\% are complex constraints. 
Constraints of additional 14\% of the constraint types are \emph{complex constraints} as well which can be simplified and therefore formulated as \emph{simple constraints} if additional constraining elements are introduced to cover them.

The properties describing a simple constrained are very structural. The central property is the \emph{constraining element} which refers to one of 103 constraining elements described in our technical report \cite{BoschNolleAcarEckert2015}. Constraining elements are for example taken from Description Logics, another concrete example would be 'REGEX' where a regular expression is checked against some property value. In most cases, constraining elements directly correspond to a constraint type, sometimes (as for REGEX) they are shared by several constraint types. Complex constraints again need several constraining elements to be expressed.

@@

A cornerstone of the framework is the generic representation of a constraint, which can often be done using \emph{Description Logics (DL)}, as for the \emph{minimum qualified cardinality restrictions}: {\small\ms{Publication $\sqsubseteq$ $\geq$1 author.Person}}

It turned out that 64\% of the 81 constraint types are actually expressible in DL. Only for the remaining 36\%, other means, i.e., other constraining elements, had to be identified. This is not surprising if we consider that OWL is based on Description Logics. When we talk about using Description Logics to represent constraints, we have to establish once more that the semantics of OWL and Description Logics differ from the semantics of constraint languages regarding the open world assumption (OWA) and the non-unique name assumption (nUNA). Both are usually assumed when dealing with OWL or DL, whereas validation usually assumes a closed world (CWA) and unique naming (UNA), i.e., if a desired property is missing, this leads to a violation and if two resources are named differently, they are assumed to be different resources.

@@

The \emph{minimum qualified cardinality restriction (R-75)} {\small\ms{Publication $\sqsubseteq$ $\geq$1 author.Person,}}
which restricts publications to have at least one author which must be a person,
is an example of a simple constraint on \emph{author}
which holds for all individuals of the class \emph{Publication}.
Table \ref{tab:property-constraint-cardinality-restriction} displays how the simple constraint is generically represented using the RDF-CV. Note that instead of the description logics construct $\geq$, the constraining element \emph{minimum qualified cardinality restriction} may be used.

@@

\subsection{Mapping implementation}

@@

\subsection{Constraint transformation}

@@

OWL is an expressive language for which description logics provides the foundational basis and which offers knowledge representation and reasoning services. Validation, however, is not the primary purpose of its design which has lead to claims that OWL cannot be used for validation. In practice, however, OWL is well-spread and RDFS/OWL constructs are widely used to tell people and applications about how valid instances should look like. In general, RDF documents follow the syntactic structure and the semantics of RDFS/OWL ontologies which could therefore not only be used for reasoning but also for validation.

>>>>

\section{Towards a Framework} 
\label{sec:vocabulary}

@@

\subsection{Building Blocks}

At the core, we use a very simple conceptual model for constraints (see Figure \ref{fig:RDF-CV-conceptual-model}), using a small lightweight vocabulary called \emph{RDF Constraints Vocabulary (RDF-CV)}\footnote{Online available at: \url{https://github.com/boschthomas/RDF-Constraints-Vocabulary}}.\tb{ToDo: actualize vocabulary}
\begin{figure}[H]
	\centering
		\includegraphics[width=0.80\textwidth]{images/RDF-CV.png}
	\caption{\emph{RDF Constraints Vocabulary (RDF-CV)} Conceptual Model}
	\label{fig:RDF-CV-conceptual-model}
\end{figure}

\emph{RDF constraints} are either simple constraints or complex constraints. \emph{Simple constraints} denotes the set of atomic constraints with respect to a single constraining element -- we will come to the notion of a constraining element in a second. In contrast, there are \emph{complex constraints}, i.e., the set of constraints which are created out of simple and/or other complex constraints. This structure therefore allows to build complex constraints out of other (simple or complex) constraints. Regarding our database of constraint types, 60\% of the constraint types are used to instantiate simple constraints and 26\% complex constraints. 
Constraints of additional 14\% of the constraint types are complex constraints as well which can be simplified and therefore formulated as simple constraints if additional constraining elements are introduced to cover them.

The properties describing a simple constrained are very structural. The central property is the \emph{constraining element} which refers to one of 103 constraining elements described in our technical report \cite{BoschNolleAcarEckert2015}. Constraining elements are for example taken from Description Logics, another concrete example would be REGEX where a regular expression is checked against some property value. In most cases, constraining elements directly correspond to a constraint type, sometimes (as for REGEX) they are shared by several constraint types. Complex constraints again need several constraining elements to be expressed.

@@

A cornerstone of the framework is the generic representation of a constraint, which can often be done using \emph{Description Logics (DL)} \cite{Kroetzsch2012,Baader-2003,Baader-Nutt-2003}, as for the \emph{minimum qualified cardinality restrictions}: {\small\ms{Publication $\sqsubseteq$ $\geq$1 author.Person.}}  This way, the knowledge representation formalism DL with its well-studied theoretical properties provides the foundational basis for the framework.

It turned out that 64\% of the 81 constraint types are actually expressible in DL. Only for the remaining 36\%, other means, i.e., other constraining elements, had to be identified. This is not surprising if we consider that OWL is based on DL. When we talk about using DL to represent constraints, we have to establish once more that the semantics of OWL and DL differ from the semantics of constraint languages regarding the open world assumption (OWA) and the non-unique name assumption (nUNA). Both are usually assumed when dealing with OWL or DL, whereas validation usually assumes a closed world (CWA) and unique naming (UNA), i.e., if a desired property is missing, this leads to a violation and if two resources are named differently, they are assumed to be different resources.

@@

The \emph{minimum qualified cardinality restriction (R-75)} {\small\ms{Publication $\sqsubseteq$ $\geq$1 author.Person,}}
which restricts publications to have at least one author which must be a person,
is an example of a simple constraint on \emph{author}
which holds for all individuals of the class \emph{Publication}.
Table \ref{tab:property-constraint-cardinality-restriction} displays how the simple constraint is generically represented using the RDF-CV. Note that instead of the DL construct $\geq$, the constraining element \emph{minimum qualified cardinality restriction} may be used.

@@

\subsection{Mapping Implementation}

@@

\subsection{Constraint Transformation}

@@

OWL is an expressive language for which DL provides the foundational basis and which offers knowledge representation and reasoning services. Validation, however, is not the primary purpose of its design which has lead to claims that OWL cannot be used for validation. In practice, however, OWL is well-spread and RDFS/OWL constructs are widely used to tell people and applications about how valid instances should look like. In general, RDF documents follow the syntactic structure and the semantics of RDFS/OWL ontologies which could therefore not only be used for reasoning but also for validation.
